Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns with a Visual-Analytics Approach

### 2016-09-09 MovePattern_IJGI/IJGI_revision/Twitter_MovementPatterns_VisualAnalytics_v2.tex
draft

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\cite{belik2011natural}.
Earlier research efforts relied on low-resolution mobility data to understand human mobility patterns, such as using census records to study human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
However, such mobility data do not provide detailed human movements with fine-grained spatial and temporal granularity, which are usually aggregated and therefore are limited to capture mobility patterns of individuals~\cite{gonzalez2008understanding,Jurdak2015}.
In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, emerging as a new mobility data source, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints in the form of real-world user trails and footprints~\cite{thatcher2014living}.
A significant advantage of utilizing LBSM data streams as proxies for studying human mobility patterns is the large spatial coverage.
For instance, researchers have used geo-located Twitter data for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible for other mobility datasets (e.g., GPS traces and mobile phone call records).
Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}, the publicly available LBSM data streams offer unique opportunities for conducting reproducible and comparative scientific findings across different geographic regions.

Many recent studies have adopted the LBSM data streams to study human mobility patterns.
For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects in the collective user movements~\cite{gonzalez2008understanding}, which were used to reveal different travel modes~\cite{Jurdak2015}, travel demands~\cite{wu2014intra,hasan2013understanding}, and the impact of social connections~\cite{cho2011friendship}.
These studies have provided strong supports for using LBSM data as proxies for studying mobility patterns of individuals and valuable insights into human mobility dynamics.
However, the variations of movements in different spatial scales and temporal ranges are neglected in these studies, where the measurements of distances are either fixed in a certain time range or to a specific geographic region.
For instances, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national levels) are lacking.
Such insights are critical to advance our understandings of the collective mobility patterns for various applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
On the other hand, while the high-resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data-intensive challenges for developing multi-scale spatiotemporal analysis approaches to dealing with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales~\cite{tsou2015}.

In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from 1$^{st}$ January to 31$^{st}$ December, 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
This framework is implemented based on high-performance distributed computing environment using Apache Hadoop\footnote{http://hadoop.apache.org/}, which is an open source software framework to enable distributed processing of large datasets across computing clusters.
Enabled by this framework, we have performed a set of statistical analysis to understand multi-scale spatiotemporal Twitter user mobility patterns. 
We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions.
In particular, Twitter user mobility patterns measured by user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
In particular, our approach provides an interactive 3D virtual globe web mapping interface to enable exploratory geo-visual analytics for understanding the detailed Twitter user movement flows within a given spatial scale and time window.

@@

However, it is worth noting that there are some limitations and complexities in directly using LBSM data for studying human mobility patterns.
For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place.
There is a potential mismatch regarding the representativeness of the overall population since not all people use social media or send geo-located messages~\cite{kung2014exploring}, the demographic information of the Twitter users cannot be easily identified.
The derived mobility patterns may lead to an over or under-representation of the real-world human mobility patterns.
Many studies started to look into the demographic information of LBSM data, in particular Twitter data~\cite{mitchell2013geography,longley2015geotemporal}.
Although the used methods are still arguable, these issues certainly require us to pose stricter criteria in understanding human mobility patterns using geo-located Twitter data.
On the other hand, geo-located Twitter dataset presents some unique advantages that make it a valuable proxy for studying human mobility patterns.
For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\cite{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\cite{hawelka2014geo}, which is almost impossible for other mobility datasets.
More importantly, by continuously monitoring the geo-located Twitter data streams with large volume of detailed and frequently updated spatiotemporal records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements), which is one of the motivations for this study.

\subsection{Data-intensive challenges for multi-scale geo-visual analytics}
Mobility data are essentially a collection of spatiotemporal records of people re-allocating across the geographic space.
To study mobility patterns of individuals, a space-time trajectory of each individual user should be modeled and constructed to quantify the collective movements over space and time.
Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of user displacements and radius of gyrations of individuals, to study the mobility dynamics.
At the same time, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\cite{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal ranges.
For example, a geo-visualization approach was used to study human activity patterns, where user trajectories are mapped in a 3D space ordered by timestamps in the third dimension~\cite{kwan2004geovisualization}.
While such an approach enables visualization of individual trajectories, its capability is limited in dealing with large-volume movement datasets~\cite{andrienko2007designing}.
Instead of directly visualizing individual user trajectories, a space-time cube approach was proposed to analyzing and visualizing the collective trajectories.
It provides flexibilities in setting up both spatial scales and temporal ranges, and therefore is used to study mobility patterns across different spatial units (e.g. countries, states, and cities, etc.) and identify the changes over space and time~\cite{maceachren2001research, maceachren2004maps}.
In this regard, visual-analytics methods are proposed to better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\cite{andrienko2007designing,andrienko2007visual}.
Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\cite{andrienko2007designing}.
Employing visual-analytics methods dealing with massive movement datasets is not only beneficial for optimizing visualizations but also provides a great deal of flexibilities for performing statistical analysis in seeking mobility patterns with different level of spatiotemporal details.

@@

\section{Materials and Methods}
\subsection{Geo-located Twitter data}
Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at.
In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
To ensure complete coverage over the continuous United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2 GB in size) collected per day.
We have collected more than 1.3 billion geo-located tweets from 1$^{st}$ January to 31$^{st}$ December, 2014 with 6,147,430 Twitter users and 1 TB in file size.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.6\linewidth]{./figures/Overall_Architecture222}
\caption{The overall system architecture of the framework}
\label{fig:overall_archi}
\end{figure}
\FloatBarrier

@@

\subsection{Multi-level spatiotemporal trajectory aggregation}
An important strategy for visual-analytics methods to deal with massive movement datasets is performing spatial aggregations to provide different levels-of-detail~\cite{andrienko2007designing,andrienko2007visual}.
It is similar to the map generation approach that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest~\cite{buttenfield1991map}.
To enable aggregating Twitter trajectories into multiple spatial scales, we have extended the hierarchical space-time cube model developed in~\cite{cao2014scalable}, where we partitioned the geographic space of the continuous United States into 10 hierarchical spatial layers. 
To be specific, the state boundaries of the continuous United States are treated as the base layer (i.e. level 0) for aggregating state-level Twitter user movements, Alaska and Hawaii are excluded for the consideration of better visualization effects in the mapping interface of the framework.
We then created an hierarchical fishnet by diving the study region into regular cells, where the finest level (level 10) consists 1 km $\times$ 1 km cells.
Such a cell size is consistent with the spatial resolution in landscan\footnote{http://web.ornl.gov/sci/landscan/} product for measuring the global population density.
In our case, the cell size for level i-1 is twice of the size in level i.
Figure~\ref{fig:multilevel} illustrates an hierarchical fishnet spatial units for mapping multi-level Twitter user movements.
Note that any predefined geographic boundaries can be used and appended in this framework to show different level-of-detailed movements (e.g., national-level and census-tract level), in our case, we replaced the level 8 fishnet layer with the US county boundaries.

To perform a multi-level spatial aggregation of the Twitter user trajectories using hierarchical spatial layers, each location in a user's trajectory is redistributed to the corresponding spatial units.
A MapReduce algorithm for the spatial aggregation is implemented, where the ID of unit in each spatial layer (e.g., polygon in state and country layer and cell in the rest) is treated as key in the at the map stage.
It performs a ``point-in-polygon" geospatial operation to determine which polygon the point belongs to.
If the location does not belong to any polygon, it will be dropped, which is how we used the geographic boundaries of the continuous United States to filer the raw tweet collection that initially covered the North America and kept the ``domestic" ones.
To optimize the ``point-in-polygon" determination without comparing the location with every polygon in the spatial layer, we also created a Quad-Tree~\cite{samet1984quadtree} for each spatial layer to speed up the process.
Finally, the reducers generate two data outputs: (1) reconstructed space-time Twitter user trajectories at each spatial level (2) movement flows in the form of in and out movement flux between the spatial units.
The movement flows are stored in the database for interactive explorations in the 3D web mapping interface, whereas the re-constructed trajectories can be further processed to produce distance measures at different spatial scales, which is illustrated as fellows:
\newline

@@

\section{Multi-scale spatiotemporal Twitter user mobility patterns}
\subsection{Spatiotemporal Twitter user mobility patterns}
The situation of using geo-located tweets as proxies to infer people's movements is complex as users' tweeting behavior can be significantly different from one to another, in particular, the frequency and time-interval between two consecutive tweets.
For example, some people may tweet once a day while others do more; some people may tweet regularly while others do not.  
These tweeting behaviors are expected as such human dynamics are also seen in the mobile phone call data~\cite{gonzalez2008understanding}. 
Many studies have carried out data collection within a certain time period (e.g., a year in our case).
However, as the geo-located tweets were collected in a continuous fashion, it is necessary to examine the sensitivities regarding these behaviors to make sure we are not just capturing a random snapshot from the whole data streams.

In this study, we have analyzed the cumulative distribution of the frequency Twitter users visiting different locations in year 2014 (and every month), which uses the methods developed in~\cite{clauset2009power}. 
The frequency is summarized based on the trajectories of individuals extracted from a monthly time span.
Note that different groups of Twitter users may exist in each month. 
It appears that the distribution of the collective Twitter user visitation behaviors in year 2014 follows a two-tiered power law distributions (shown in Figure~\ref{fig:visitation}, where the majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$ and the $\alpha$ value is 1.32, and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $p(x)\sim x^{-\alpha}$ with $\alpha$ value is 3.5.
This finding is consistent across all 12 months, with the mean $\alpha$ value as 1.34 $ \pm$  0.05 (standard deviation) and the mean $\lambda$ value as 0.00178 $ \pm$  0.0002 (standard deviation).

@@

In particular, as it is shown in Figure~\ref{fig:displacement} (a), the probability distribution of the overall displacements is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10~m$ from [10 m, 70 m] (accounting for 2 $\%$ of the population), $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min}=100~m$ from [100 m, 80 km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80 km] (accounting for 5 $\%$ of the population).
In addition, the displacement in the distance bound from 100 m and 80 km in Figure~\ref{fig:displacement} (b) can be further approximately by two power-law distributions with a cutting point at 5 km (53$\%$ distances are less than 5 km and 40$\%$ distances between 5 km and 80 km), which indicates two different travel modes, such as inter- or intra-city movements.
Overall, the fitting functions with different distance bounds suggest the existence of multi-scale or multi-modal mobility patterns~\cite{Jurdak2015} of the Twitter users in the continuous United States, for example the displacements larger than 80 km could be related to inter-state travels or travel by flight.

The probability distribution of radius of gyrations of individuals at the national level (Figure~\ref{fig:gyration} (a)) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10~m$ from [10 m, 50 m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50 m, 30 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30 km].
In particular, the radius of gyration between 50 m and 30 km can be further approximately by two power law distributions with a cutting point at 6 km (Figure~\ref{fig:gyration} (b)), which suggest two main types of spatial coverage of from the collected Twitter users in the continuous United States.
The distribution shows that around $10\%$ the tweet population has a radius of gyration less than 50 meters, which indicates those twitter users mostly tweet at a particular place, such as home or office;  around 60$\%$ of the population has a radius of gyration less than 30 km, which indicates that most of the collected Twitter user movements are ``short" distances, e.g., within a city locale. Note that the accuracy of these values for defining the distance bound depends on the accuracy of the location information of each geo-located tweet.

@@

The above analysis of Twitter user mobility patterns mainly focus on the spatiotemporal aspects.
Our framework provides the flexibility to aggregate and extract Twitter user trajectories in a specific spatial scale and re-produce the analysis. 
In particular, as it is evident from the above analysis that there are multi-scale or multi-modal Twitter user mobility patterns, this framework can help further look into the mobility pattern regarding how Twitter users move across different spatial scales and temporal ranges, which is measured by the movement flows between these spatial units.
In this case, we demonstrate the inter-state mobility patterns by using the framework to capture the movement flows between the states.
Note that the movement flows can be summarized across all the 10 spatial layers in the framework.
We tested the overall distribution of the movement flows (in the form of weighted in-degree and out-degree of a graph, where each state is treated as a node) among different states in year 2014.
We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states.
It indicates that the Twitter population is not proportional to account the movement flux between the states, which may provide some insights for other researchers in studying social-economical aspects of the migration dynamics.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\cite{belik2011natural}.
Earlier research efforts relied on low-resolution mobility data to understand human mobility patterns, such as using census records to study human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
However, such mobility data do not provide detailed human movements with fine-grained spatial and temporal granularity, which are usually aggregated and therefore are limited to capture mobility patterns of individuals~\cite{gonzalez2008understanding,Jurdak2015}.
In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, emerging as a new mobility data source, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints in the form of real-world user trails and footprints~\cite{thatcher2014living}.
A significant advantage of utilizing LBSM data streams as proxies for studying human mobility patterns is the large spatial coverage.
For instance, researchers have used geo-located tweets for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible for other mobility datasets (e.g., GPS traces and mobile phone call records).
Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}, the publicly available LBSM data streams offer unique opportunities for conducting reproducible and comparative scientific findings across different geographic regions.

Many recent studies have adopted LBSM data streams to study human mobility patterns.
For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects in the collective user movements~\cite{gonzalez2008understanding}, which were used to reveal different travel modes~\cite{Jurdak2015}, travel demands~\cite{wu2014intra,hasan2013understanding}, and the impact of social connections~\cite{cho2011friendship}.
These studies have provided strong supports for using LBSM data as proxies for studying mobility patterns of individuals and valuable insights into human mobility dynamics.
However, the variations of movements in different spatial scales and temporal ranges are neglected in these studies, where the measurements of distances are either fixed in a certain time range or to a specific geographic region.
For instances, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national levels) are lacking.
Such insights are critical to advance our understandings of the collective mobility patterns for various applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
On the other hand, while the high-resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data-intensive challenges for developing multi-scale spatiotemporal analysis approaches to dealing with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales~\cite{tsou2015}.

In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from 1$^{st}$ January to 31$^{st}$ December, 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
This framework is implemented based on high-performance distributed computing environment using Apache Hadoop\footnote{http://hadoop.apache.org/}, which is an open source software framework to enable distributed processing of large datasets across computing clusters.
Enabled by this framework, we have performed a set of statistical analysis to understand multi-scale spatiotemporal Twitter user mobility patterns. 
We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions.
In particular, Twitter user mobility patterns measured by user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
In addition, our approach provides an interactive 3D virtual globe web mapping interface to enable exploratory geo-visual analytics for understanding the detailed Twitter user movement flows within a given spatial scale and time window.

@@

However, it is worth noting that there are some limitations and complexities in directly using LBSM data for studying human mobility patterns.
For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place.
Although geo-located tweets tend to provide geo-locations with high position resolution as aforementioned~\cite{Jurdak2015}, the information regarding the quality of the geo-locations is absent in each tweet.
This will contribute to the uncertainties in calculating the distance of Twitter user movements, especially in densely built environments.   
There is also a potential mismatch regarding the representativeness of the overall population since not all people use social media or send geo-located messages~\cite{kung2014exploring}, the demographic information of the Twitter users cannot be easily identified.
The derived mobility patterns may lead to an over or under-representation of the real-world human mobility patterns.
Many studies started to look into the demographic information of LBSM data, in particular Twitter data~\cite{mitchell2013geography,longley2015geotemporal}.
Although the used methods are still arguable, these issues certainly require us to pose stricter criteria in understanding human mobility patterns using geo-located Twitter data.
On the other hand, geo-located Twitter dataset presents some unique advantages that make it a valuable proxy for studying human mobility patterns.
For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\cite{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\cite{hawelka2014geo}, which is almost impossible for other mobility datasets.
More importantly, by continuously monitoring the geo-located Twitter data streams with large volume of detailed and frequently updated spatiotemporal records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements), which is one of the motivations for this study.

\subsection{Data-intensive challenges for multi-scale geo-visual analytics}
Mobility data are essentially a collection of spatiotemporal records of people re-allocating across the geographic space.
To study mobility patterns of individuals, a space-time trajectory of each individual user should be modeled and constructed to quantify the collective movements over space and time.
Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of user displacements and radius of gyrations of individuals, to study the mobility dynamics.
Indeed, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\cite{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal ranges.
For example, a geo-visualization approach was used to study human activity patterns, where user trajectories were mapped in a 3D space ordered by timestamps in the third dimension~\cite{kwan2004geovisualization}.
While such an approach enables visualization of individual trajectories, its capability is limited in dealing with large-volume movement datasets~\cite{andrienko2007designing}.
Instead of directly visualizing an individual user's trajectories, a space-time cube approach was proposed to analyzing and visualizing the collective trajectories.
It provides flexibilities in setting up both spatial scales and temporal ranges, and therefore is used to study mobility patterns across different spatial units (e.g., countries, states, and cities, etc.) and identify the changes over space and time~\cite{maceachren2001research, maceachren2004maps}.
In this regard, visual-analytics methods are proposed to better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\cite{andrienko2007designing,andrienko2007visual}.
Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\cite{andrienko2007designing}.
Employing visual-analytics methods dealing with massive movement datasets is not only beneficial for optimizing visualizations but also provides a great deal of flexibilities for performing statistical analysis in seeking mobility patterns with different level of spatiotemporal details.

@@

\section{Materials and Methods}
\subsection{Geo-located Twitter data}
Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at.
In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
To ensure complete coverage over the continuous United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2 GB in size) collected per day.
We have collected more than 1.3 billion geo-located tweets from 1$^{st}$ January to 31$^{st}$ December, 2014 with 6,147,430 Twitter users and 1 TB in file size.
In particular, this data collection of year 2014 was originally used to map the spatial spread of flu in North America during the time period~\cite{padmanabhan2014flumapper}.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.55\linewidth]{./figures/Overall_Architecture222}
\caption{The overall system architecture of the framework}
\label{fig:overall_archi}
\end{figure}
\FloatBarrier

@@

\subsection{Multi-level spatiotemporal trajectory aggregation}
An important strategy for visual-analytics methods to deal with massive movement datasets is performing spatial aggregations to provide different levels-of-detail~\cite{andrienko2007designing,andrienko2007visual}.
It is similar to the map generation approach that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest~\cite{buttenfield1991map}.
To enable aggregating Twitter trajectories into multiple spatial scales, we have extended the hierarchical space-time cube model developed in~\cite{cao2014scalable}, where we partitioned the geographic space of the continuous United States into 10 hierarchical spatial layers and each space-time cube is created with a fixed time window of a week interval. 
Specifically, the state boundaries of the continuous United States are treated as the base layer (i.e. level 0) for aggregating state-level Twitter user movements, Alaska and Hawaii are excluded for the consideration of better visualization effects in the mapping interface of the framework.
We then created an hierarchical fishnet by diving the study region into regular cells, where the finest level (level 10) consists 1 km $\times$ 1 km cells.
Such a cell size is consistent with the spatial resolution in landscan\footnote{http://web.ornl.gov/sci/landscan/} product for measuring the global population density.
In our case, the cell width/height for level i-1 is twice of the size in level i.
Figure~\ref{fig:multilevel} illustrates an hierarchical fishnet spatial units for mapping multi-level Twitter user movements.
Note that any predefined geographic boundaries can be used and appended in this framework to show different level-of-detailed movements (e.g., national-level and census-tract level), in our case, we replaced the level 8 fishnet layer with the US county boundaries.

To perform a multi-level spatial aggregation of the Twitter user trajectories using hierarchical spatial layers, each location in a user's trajectory is redistributed to the corresponding spatial units.
A MapReduce algorithm for the spatial aggregation is implemented, where the ID of unit in each spatial layer (e.g., polygon in state and country layer and cell in the rest) is treated as key in the at the map stage.
It performs a ``point-in-polygon'' geospatial operation to determine which polygon the point belongs to.
If the location does not belong to any polygon, it will be dropped, which is how we used the geographic boundaries of the continuous United States to filer the raw tweet collection that initially covered the North America and kept the ``domestic'' ones.
To optimize the ``point-in-polygon'' determination without comparing the location with every polygon in the spatial layer, we also created a Quad-Tree~\cite{samet1984quadtree} for each spatial layer to speed up the process.
Finally, the reducers generate two data outputs: (1) reconstructed space-time Twitter user trajectories at each spatial level (2) movement flows in the form of in and out movement flux between the spatial units.
The movement flows are stored in the database for interactive explorations in the 3D web mapping interface, whereas the re-constructed trajectories can be further processed to produce distance measures at different spatial scales, which is illustrated as fellows:
\newline

@@

\section{Multi-scale spatiotemporal Twitter user mobility patterns}
\subsection{Spatiotemporal Twitter user mobility patterns}
The situation of using geo-located tweets as proxies to infer people's movements is complex as users' tweeting behavior can be significantly different from one to another, in particular, the frequency and time-interval between two consecutive tweets.
For example, some people may tweet once a day while others do more; some people may tweet regularly while others do not.  
These tweeting behaviors are expected as such human dynamics are also seen in the mobile phone call data~\cite{gonzalez2008understanding}. 
Many studies have carried out data collection within a certain time period (e.g., a year in our case).
However, as the geo-located tweets were collected in a continuous fashion, it is necessary to examine the sensitivities regarding these behaviors to ensure we are not just capturing a random snapshot from the whole data streams.

In this study, we have analyzed the cumulative distribution of the frequency Twitter users visiting different locations in year 2014 (and every month), which uses the methods developed in~\cite{clauset2009power}. 
The frequency is summarized based on the trajectories of individuals extracted from a monthly time span.
Note that different groups of Twitter users may exist in each month. 
It appears that the distribution of the collective Twitter user visitation behaviors in year 2014 follows a two-tiered power law distributions (shown in Figure~\ref{fig:visitation}.
The majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$, where $x$ is the number of visited locations and the $\alpha$ value is 1.32.
The tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $p(x)\sim x^{-\alpha}$ with $\alpha$ value is 3.5.
This finding is consistent across all 12 months, with the mean $\alpha$ value as 1.34 $ \pm$  0.05 (standard deviation) and the mean $\lambda$ value as 0.00178 $ \pm$  0.0002 (standard deviation).

@@

Figure~\ref{fig:displacement} (a) shows the probability distribution of the overall displacements, which is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10~m$ from [10 m, 70 m] (accounting for 2 $\%$ of the population), $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min}=100~m$ from [100 m, 80 km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80 km] (accounting for 5 $\%$ of the population).
In addition, the displacement in the distance bound from 100 m and 80 km in Figure~\ref{fig:displacement} (b) can be further approximately by two power-law distributions with a cutting point at 5 km (53$\%$ distances are less than 5 km and 40$\%$ distances between 5 km and 80 km), which indicates two different travel modes, such as inter- or intra-city movements.
Overall, the fitting functions with different distance bounds suggest the existence of multi-scale or multi-modal mobility patterns~\cite{Jurdak2015} of the Twitter users in the continuous United States, for example, the displacements larger than 80 km could be related to inter-state travels and stronger distance decay effects are observed in longer distance travels.

The probability distribution of radius of gyrations of individuals at the national level (Figure~\ref{fig:gyration} (a)) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10~m$ from [10 m, 50 m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50 m, 30 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30 km].
In particular, the radius of gyration between 50 m and 30 km can be further approximately by two power law distributions with a cutting point at 6 km (Figure~\ref{fig:gyration} (b)), which suggest two main types of spatial coverage of from the collected Twitter users in the continuous United States.
The distribution shows that around $10\%$ the tweet population has a radius of gyration less than 50 meters, which indicates those twitter users mostly tweet at a particular place, such as home or office;  around 60$\%$ of the population has a radius of gyration less than 30 km, which indicates that most of the collected Twitter user movements are ``short'' distances, e.g., within a city locale. Note that the accuracy of these values for defining the distance bound depends on the accuracy of the location information of each geo-located tweet.

@@

The above analysis of Twitter user mobility patterns mainly focuses on the spatiotemporal aspects.
Our framework provides the flexibility to aggregate and extract Twitter user trajectories in a specific spatial scale and re-produce the analysis.
In particular, as it is evident from the above analysis that there are multi-scale or multi-modal Twitter user mobility patterns, this framework can help further look into the mobility pattern regarding how Twitter users move across different spatial scales and temporal ranges, which is measured by the movement flows between these spatial units.
The movement flows are obtained by aggregating the movements that started from and ended in the corresponding spatial units within the giving time frame.
In this case, we demonstrate the inter-state mobility patterns by using the framework to capture the movement flows between the states.
Note that the movement flows can be summarized across all the 10 spatial layers in the framework.
We tested the overall distribution of the movement flows (in the form of weighted in-degree and out-degree of a graph, where each state is treated as a node) among different states in year 2014.
We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states.
It indicates that the Twitter population is not proportional to account the movement flux between the states, which may provide some insights for other researchers in studying social-economical aspects of the migration dynamics.
